\documentclass{report}
\usepackage[utf8]{inputenc}

% Títulos automáticos en Ingles
\usepackage[english]{babel}

% Soporte para buenas urls e hipervínculos entre secciones
\usepackage{hyperref}

% Citas y referencias en formato APA
% Si quiere las citas y referencias en IEEE comente esta línea
\usepackage{apacite}

% Imágenes y figuras
\usepackage{graphicx}

% Código fuente con números de línea
\usepackage{listings}
% Puede cambiar el lenguaje de código fuente
% https://www.overleaf.com/learn/latex/code_listing#Supported_languages
\lstset{
    language=C,
    basicstyle=\footnotesize,
    numbers=left,
    stepnumber=1,
    showstringspaces=false,
    tabsize=1,
    breaklines=true,
    breakatwhitespace=false,
}


\def \unidad{Universidad Tecnológica de Tijuana }
\def \programa{Ingeniería En Desarrollo Y Gestión De Software }
\def \curso{Aplicaciones Web Progresivas}
\def \titulo{Tools and Developments of PWAs}

\def \autores{
    Mercado Juarez Angel Hayr\\
    0319124541@ut-tijuana.edu.mx \\
    0319124541\\
    
    \vspace{0.5cm}
    
    Teacher \\
    Dr. Ray Brunett Parra\\
}
\def \fecha{10 January 2024}
\def \lugar{
    Tijuana B.C, 
   México
}

% Inicia el documento 
\begin{document}

% Inserta la portada del documento
\input{portada}

\tableofcontents

\chapter{Tools and Developments of PWAs}\label{Tools and Developments of PWAs}
\section{Introduction}\label{intro}
PWAs are a relatively new technology, but they are quickly gaining popularity. They offer a number of advantages over traditional web apps, including: 
\begin{itemize}
    \item Offline support: PWAs can be used even when the user is not connected to the internet.
    \item Push notifications: PWAs can send push notifications to the user, even when the app is not in use.
    \item Native app-like experiences: PWAs can be launched from the user's home screen and can be used with system-level features, such as notifications and permissions.
\end{itemize}
\section{Requirements}\label{Requirements}

To create a PWA, developers must first ensure that their web application meets the following requirements .\cite{mdn23}
\begin{itemize}
    \item The application must be built using web technologies, such as HTML, CSS, and JavaScript.
    \item The application must be responsive and should work well on a variety of devices and screen sizes.
    \item The application must be progressive, meaning that it should provide a good user experience even if it is not installed on the user's device.
\end{itemize}

\section{Browsers}\label{Browsers}

PWAs are supported by most modern browsers, including: 

\begin{itemize}
    \item Chrome
    \item Firefox
    \item Edge
    \item Safari
\end{itemize}
In addition to these browsers, there are also a number of third-party PWA browsers available, such as: 

\begin{itemize}
    \item PWABuilder
    \item PWAify
    \item PWA Launcher
\end{itemize}

\section{Development tools}\label{Development tools}

There are a number of development tools available to help developers create PWAs. These tools can help developers to: \cite{w3c23}

\begin{itemize}
    \item Create a PWA-compatible web application
    \item Test and debug a PWA
    \item Deploy a PWA to the web
\end{itemize}

Some popular PWA development tools include: 
\begin{itemize}
    \item Create React App
    \item Angular CLI
    \item Ionic Framework
\end{itemize}

\section{Benefits of using PWAs}\label{Benefits of using PWAs}
PWAs offer a number of benefits over traditional web apps, including: \cite{google23}

\begin{itemize}
    \item Better user experience: PWAs can provide a better user experience than traditional web apps, thanks to features such as offline support and push notifications
    \item Increased engagement: PWAs can help to increase user engagement, thanks to features such as push notifications and native app-like experiences
    \item Improved search engine optimization (SEO): PWAs can improve a web application's SEO, thanks to features such as service workers and app manifests
\end{itemize}



\section{Conclusion}\label{Conclusion}
PWAs are a powerful new technology that can offer a number of advantages over traditional web apps. They are a good choice for web applications that need to provide a good user experience, increase engagement, or improve SEO.


% Estilo de bibliografía APA
% Si quiere usar el estilo IEEE comente esta línea
\bibliographystyle{apacite}

% Descomente esta línea para usar el estilo de bibliografía IEEE
%\bibliographystyle{ieeetr}
\bibliography{referencias}

\end{document}
